Think again?\\ The amount of mental simulation tracks uncertainty in the outcome

### 2015-05-01 manuscript.tex
Remaining grant information, a few more minor edits

We consider binary (or two-alternative forced choice) decisions, where an agent must choose one of two hypotheses, $H_0$ or $H_1$.
In the case of the task in Figure \ref{fig:experiment}, $H_1$ is the hypothesis that the ball goes in, and $H_0$ is the hypothesis that it does not. 
The agent may take samples $X_i$ from a Bernoulli distribution with an unknown parameter $p$ (the probability of sampling evidence for $H_1$), and from these samples estimate the probability that $H_1$ is correct: $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples. 
Then, the decision rule which minimizes the probability of error is $\hat{H}(X_1,\ldots{},X_N)=H_0$ when $\hat{p}<0.5$ and $\hat{H}(X_1,\ldots{},X_N)=H_1$ when $\hat{p}>0.5$.

@@

In order to ensure that participants never saw the same initial animation twice, we used a latin-square design of Initial Animation $\times$ Trial Type $\times$ Hole Size.
Thus, each participant saw each initial animation once, each trial type 12 times, and each hole size 24 times.
This also ensured that the ball would go through the hole half the time, so that participants would not be biased to respond either way.
Additionally, there were seven instruction trials and eight control trials, which were the same for all participants.
The control trials were designed to be easy and were either of type ``straight hit'' (with a hole size of either 300px or 350px) or ``far miss'' (with a hole size of 100px).
Thus, participants saw a total of 63 trials.

@@

This work was supported by a NSF GRF awarded to JBH, a UCSD Chancellor’s Interdisciplinary Collaboratories grant awarded to KAS, NSF CPS grant 1239323, and \TODO{}.

>>>>

We consider binary (or two-alternative forced choice) decisions, where an agent must choose one of two hypotheses, $H_0$ or $H_1$.
In the case of the task in Figure \ref{fig:experiment}, $H_1$ is the hypothesis that the ball goes in, and $H_0$ is the hypothesis that it does not. 
The agent may take samples $X_i$ from a Bernoulli distribution with an unknown parameter $p$ (the probability of sampling evidence for $H_1$), and from these samples estimate the probability that $H_1$ is correct: $\hat{p}=\frac{1}{N}\sum_{i=1}^N X_i$, where $N$ is the total number of samples. 
Then, the decision rule that minimizes the probability of error is $\hat{H}(X_1,\ldots{},X_N)=H_0$ when $\hat{p}<0.5$ and $\hat{H}(X_1,\ldots{},X_N)=H_1$ when $\hat{p}>0.5$.

@@

In order to ensure that participants never saw the same initial animation twice, we used a Latin square design of Initial Animation $\times$ Trial Type $\times$ Hole Size.
Thus, each participant saw each initial animation once, each trial type 12 times, and each hole size 24 times.
This also ensured that the ball would go through the hole half the time, so that participants would not be biased to respond either way.
Additionally, there were seven instruction trials and eight control trials, which were the same for all participants.
The control trials were designed to be easy and were either of type ``straight hit'' (with a hole size of either 300px or 350px) or ``far miss'' (with a hole size of 100px).
Thus, participants saw a total of 63 trials.

@@

This work was supported by a NSF GRF awarded to JBH, a UCSD Chancellor’s Interdisciplinary Collaboratories grant awarded to KAS, NSF CPS grant 1239323, and grant number N00014-13-1-0341 from the Office of Naval Research.
